### 2024-02-04 README.Rmd
change description

@@

# install.packages("devtools")
devtools::install_github("horankev/sfislands")

@@

```{r}
st_bridges(df = df_scaled_sf|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2
)  |> 
  st_manual_join_nb("Gower","St Ives") |>
  st_quickmap_contigs(title = "st_bridges contiguities: Wales & South West",
                      subtitle = "with additional st_manual_join_nb() for Gower and St Ives")
```

>>>>

``` r
# install.packages("devtools")
devtools::install_github("horankev/sfislands")
```

@@

# install.packages("devtools")
# devtools::install_github("horankev/sfislands")

@@

```{r}
st_bridges(df = df_scaled_sf|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2
)  |> 
  st_manual_join_nb("Gower","St Ives")
```
